Improvement of crash forces in structures using optimization tools.

### 2016-07-26 paper.tex
Avances

In order to facilitate the generation of an stable collapse mechanism, crash boxes usually have some triggering in certain areas. It is based on certain controlled weakening of a section of the tube so, when crushing starts, the collapse will tend to a known pattern instead of others. This is done because this stable collapse patterns give the greatest \acrlong{SEA} with reduced \acrlong{Pk}.

@@

\subsection{On the \acrlong{XFEM} and the explicit solver}
\label{sec:xfem}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/mesh_detail_coh3d_comparison}
	\caption[Detail of \acrlong{COH3D} mesh on the adhesive layer.]{Detail of \acrlong{COH3D} mesh on the adhesive layer (blue).}
	\label{fig:mesh_detail_coh3d_comparison}
\end{figure}

@@

\subsubsection{The \acrlong{COH3D}}
\label{sec:coh_elem}

As \acrlong{COH3D} were specifically formulated for adhesive modelling, among other uses, they have been widely used to model this material, in Abaqus \cite{Sadowski2010, Sadowski2011, Sadowski2014, Alvarez2014} and in other software packages \cite{Sato2000, Carlberger2007, Loureiro2010, Scattina2011, Ghasemnejad2013}, although this is not the only existing formulation \cite{Sato2000, Greve2007, Liao2011, Yang2012}. Certain stress distributions cannot be properly modelled, such as in-plane compression, but these have no interest or negligible effects. In Abaqus, these elements are denominated \acrshort{COH3D} and require that:
\begin{itemize}
	\item There can only be a single layer of elements.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/union}
	\caption[Cross section detail of the adhesive layer modelled with \acrlongpl{COH3D} between two adherends modelled with shell elements.]{Cross section detail of the adhesive layer modelled with \acrlongpl{COH3D} between two adherends modelled with shell elements. Taken from \cite{Scattina2011}.}
	\label{fig:union}
\end{figure}

>>>>

In order to facilitate the generation of an stable collapse mechanism, crash boxes usually have some triggering in certain areas. It is based on certain controlled weakening of a section of the tube so, when crushing starts, the collapse will tend to a known pattern instead of others. This is done because this stable collapse patterns give the greatest SEA with reduced Pk.

@@

\subsection{On the XFEM and the explicit solver}
\label{sec:xfem}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/mesh_detail_coh3d_comparison}
	\caption[Detail of COH3D mesh on the adhesive layer.]{Detail of COH3D mesh on the adhesive layer (blue).}
	\label{fig:mesh_detail_coh3d_comparison}
\end{figure}

@@

\subsubsection{The COH3D}
\label{sec:coh_elem}

As COH3D were specifically formulated for adhesive modelling, among other uses, they have been widely used to model this material, in Abaqus \cite{Sadowski2010, Sadowski2011, Sadowski2014, Alvarez2014} and in other software packages \cite{Sato2000, Carlberger2007, Loureiro2010, Scattina2011, Ghasemnejad2013}, although this is not the only existing formulation \cite{Sato2000, Greve2007, Liao2011, Yang2012}. Certain stress distributions cannot be properly modelled, such as in-plane compression, but these have no interest or negligible effects. In Abaqus, these elements are denominated \acrshort{COH3D} and require that:
\begin{itemize}
	\item There can only be a single layer of elements.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/union}
	\caption[Cross section detail of the adhesive layer modelled with COH3D between two adherends modelled with shell elements.]{Cross section detail of the adhesive layer modelled with COH3D between two adherends modelled with shell elements. Taken from \cite{Scattina2011}.}
	\label{fig:union}
\end{figure}
